New approaches for boosting to uniformity

### 2014-09-18 assets/paperdraft/paper_draft.tex

\title{New Approaches to Uniform Boosting}

@@

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}

@@

@@

\section{Uniformity Measurement}

\input{parts/metrics}

\section{Approaches Proposed}

\input{parts/approaches}

\section{Dataset}

\input{parts/dataset}

\section{Plots}

\input{parts/plots}

@@

\bibitem{Sjostrand:2006za}
{"Sj\"{o}strand, Torbj\"{o}rn and Mrenna, Stephen and Skands, Peter"},
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026},
{\emph{JHEP} {\bf 05} (2006) 026},
[\hepph{0603175}].

@@

\bibitem{Golonka:2005pn}
{"Golonka, Piotr and Was, Zbigniew"},
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4},
{\emph{EPJ} {\bf C45} (2006) 97-107},
[\hepph{0506026}].

@@

>>>>

\title{New approaches for boosting to uniformity}

@@

% AMS packages:

\usepackage{amsmath, amsthm, amsfonts, xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}

@@

\def\x {\ensuremath{\vec{x}}\xspace}
\def\y {\ensuremath{\vec{y}}\xspace}
\def\knn{\text{knn}}
\def\knni{\text{knn}(i)}

@@

\section{Uniformity Boosting Methods}
\input{ugb}

\section{Example Analysis}

\input{parts/dataset}
\input{parts/plots}

@@

\bibitem{ref:lhcbhlt} 
R. Aaij {\em et al.} [LHCb Trigger Group], 
{\em The LHCb trigger and its performance}, 
JINST {\bf 8}, P04022 (2013). 
[arXiv:1211.3055]

\bibitem{ref:bbdt}  
V. Gligorov and M. Williams, 
{\em Efficient, reliable and fast high-level triggering using a bonsai boosted decision tree}, 
JINST {\bf 8}, P02013 (2013). 
[arXiv:1210.6861]

\bibitem{ref:uboost} 
J. Stevens and M. Williams,
{\em uBoost: A boosting method for producing uniform selection efficiencies from multivariate classifiers}, 
JINST {\bf 8}, P12013 (2013). 
[arXiv:1305.7248]

\bibitem{Sjostrand:2006za}
{"Sj\"{o}strand, Torbj\"{o}rn and Mrenna, Stephen and Skands, Peter"},
\emph{PYTHIA 6.4 physics and manual},
\href{http://dx.doi.org/10.1088/1126-6708/2006/05/026},
{\emph{JHEP} {\bf 05} (2006) 026}.
[\hepph{0603175}]

@@

\bibitem{Golonka:2005pn}
{"Golonka, Piotr and Was, Zbigniew"},
\emph{PHOTOS Monte Carlo: a precision tool for QED corrections in $Z$ and $W$ decays},
\href{http://dx.doi.org/10.1140/epjc/s2005-02396-4},
{\emph{EPJ} {\bf C45} (2006) 97-107}.
[\hepph{0506026}]

@@

\appendix
\section{Other Flatness Loss Criteria}

Clean all this up...

%\section{Uniformity Measurement}
\input{parts/metrics}
%\section{Approaches Proposed}
\input{parts/approaches}
